Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-11 R0V0.tex
Start the proof of decomposition of the MI

An algorithm to compute the number of cliques is provided in \cite{BronKerbosch1973}.

>>>>

\begin{proof}
	The number of cliques $p$ in the $\mathscr{G}$ can be computed using the algorithm \cite{BronKerbosch1973}. The remainder of this proof is based on Section~II of \cite{PakazadHanssonAndersenEtAl2015}.

	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the cliques of the $\mathscr{G}$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$. For each index $k\in\mathbb{N}_{[1,p]}$, define the matrix $E_k\in\mathbb{R}^{\mathbin{\mathtt{card}}(\mathscr{C}_k)\times n}$ as
	\begin{equation*}
		\mathbin{\mathtt{row}}(E_k,m)=\mathbin{\mathtt{row}}(I_n,m),\forall m\in\mathbb{N}_{[1,\mathbin{\mathtt{card}}(\mathscr{C}_k)]}\;,
	\end{equation*}	
	where $\mathbin{\mathtt{row}}(E_k,m)$ stands for the $m$-th row of the matrix $E_k$, and $I_n$ is the identity matrix with dimension $n$.

\end{proof}
